\documentclass[]{andre-vechina-resume}
\usepackage{lipsum}
\begin{document}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     LAST UPDATED DATE
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     TITLE NAME
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{André}{Vechina}{\urlstyle{same}\href{http://andrevechina.com}{andrevechina.com} | LinkedIn://\href{https://www.linkedin.com/in/andrevechina}{\bf andrevechina} \\
\href{mailto:andrevechina@gmail.com}{andrevechina@gmail.com} | +351 915606584
}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     LINKS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Links}
% Facebook:// \href{https://facebook/dd}{\bf dd} \\
% Github:// \href{https://github.com/deedydas}{\bf deedydas} \\
% LinkedIn://  \href{https://www.linkedin.com/in/debarghyadas}{\bf debarghyadas} \\

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     EXPERIENCE
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\runsubsection{Blip - Paddy Power Betfair}
\descript{| Software Developer }
\location{Oct 2014 - Present | Porto, Portugal}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item
Member of a Kanban squad building several web-based internal tools, mainly using ES6+, React and Redux.
Member of a cross-location team (Porto and Dublin) working in a highly collaborative agile environment.
Quality software is one of the main concerns, code coverage is over 95\% and each feature is implemented using the BDD process.
Active part in the recruitment process, performing technical interviews.
\item
Member of a Scrum team responsible for building Betfair's Sportsbook client side rendered mobile web-application.
Development and maintenance of a +500k loc AngularJS application, as well as all its supporting web middlewares NodeJS based, capable of scaling up to over 1M active users (100k simultaneously).
Monitoring and improvement of performance and scalability issues, both for data fetching and client side rendering.
\end{tightemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\centering{
    Javascript \tdot
    React \tdot
    Redux \tdot
    React-Router \tdot
    AngularJS
    \\
    Webpack \tdot
    Grunt \tdot
    Jasmine \tdot
    Mocha \tdot
    Protractor
    \\
    Kanban \tdot
    Scrum \tdot
    Continuous Integration \tdot
    Continuous Deploy
}
\sectionsep

\runsubsection{Blip - Paddy Power Betfair}
\descript{| Software Engineer Intern}
\location{Apr 2014 - Sep 2014 | Porto, Portugal}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item
Development of Betfair's Sportsbook server side rendered websites (both desktop and mobile) built using a Spring based framework.
\end{tightemize}
\centering{
    Java \tdot
    Javascript \tdot
    Selenium
}
\sectionsep

\runsubsection{PT Inovação}
\descript{| Research Engineer Trainee}
\location{Apr 2013 – Mar 2014 | Aveiro, Portugal}
\begin{tightemize}
\item
Member of a small team that developed and integrated functional prototypes.
\item
Development and integration of a SIP WebRTC client and a SCC-AS (Service Centralization and Continuity Application Server) in a IMS environment.
\end{tightemize}
\centering{
    Javascript \tdot
    Coffescript \tdot
    Spine.js \tdot
    sipML5 \tdot
    WebRTC \tdot
    Java
}
\sectionsep

\runsubsection{Varident}
\descript{| Web Developer Intern}
\location{Jul 2011 – Sep 2011 | Somerville, NJ, USA}
\begin{tightemize}
\item
Member of a small development team that delivered custom designed business websites and created a form-builder, for the content management system developed in-house (KickStart).
\end{tightemize}
\centering{
    Javascript \tdot
    jQuery
}
\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     EDUCATION
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\runsubsection{University of Aveiro}
\descript{| Msc in Computer and Telematics Engineering}
\location{Sep 2007 - Dec 2012 | Aveiro, Portugal}
Final grade: {\color{subheadings} 15/20}
\tdot
Dissertation grade: {\color{subheadings} 17/20}\\
\location{Msc Dissertation:}
\begin{tightemize}
\item
Representation of semantic networks of biomedical terms.
\item
Development of a web platform for representation and analysis of relationships among biomedical identities.
\end{tightemize}
\centering{
    Java \tdot
    J2EE \tdot
    JSF \tdot
    Javascript
}
\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     PUBLICATIONS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}

\bibliographystyle{ieeetr}
\bibliography{publications}
\nocite{*}

\end{document}
